Sketch of DP - Bayesian Inference

### 2018-07-14 main-sketch.tex
prefer this word

In this work we present a new mechanism for differentially private Bayesian
inference where the noise is added w.r.t  a smooth
sensitivity computed with a metric on probability distributions.
We also measure the accuracy of the process by using a metric over
probability measures.  We compared the accuracy of this approach with
the one based on the $\ell_1$-norm.  We present experimental results
showing that the former outperforms the latter.

>>>>

In this work we present a new mechanism for differentially private Bayesian
inference where the noise is calibrated w.r.t  a smooth
sensitivity computed with a metric on probability distributions.
We also measure the accuracy of the process by using a metric over
probability measures.  We compared the accuracy of this approach with
the one based on the $\ell_1$-norm.  We present experimental results
showing that the former outperforms the latter.
